Output Summary

### 2020-11-20 03-post-process/output-plots.Rmd
Build in structure for scenario names
This will facilitate comparing different parameterizations of ocean survival and other things down the road

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

# read information from this model
model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output.rds")))

>>>>

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: base
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

# read information from this model
model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output-", params$scenario, ".rds")))
